|

### 2023-05-08 paper/03-methods.Rmd
outlined stability section
average strain, unsuccessful pass rush

## Average STRAIN

>>>>

Moreover, since we observe STRAIN continuously at every tenth of a second within each play, we can then compute the average STRAIN across all frames played for every pass rusher.
This can be helpful in regards to player evaluation, as we can determine the most effective pass-rushers based on their average STRAIN values.
Formally, the average STRAIN, denoted by $\overline{\text{STRAIN}}$, for pass rusher $i$ over $n$ total plays with $T$ total frames is

[CHECK THIS - is notation consistent with what we have above?]
\begin{equation}
\overline{\text{STRAIN}}_{i} = \frac{1}{n} \sum_{t=1}^T {\text{STRAIN}}_{i}(t).
\end{equation}

### 2023-05-08 paper/04-results.Rmd
added figures to the data section
average strain, unsuccessful pass rush

To illustrate our proposed metric STRAIN for pass rush evaluation, we use a play from the 2021 NFL regular season week 6 matchup between the Las Vegas Raiders and Denver Broncos, which ended with Broncos QB Teddy Bridgewater getting sacked by Raiders DE Maxx Crosby[^crosbysack].
Figure \ref{fig:fig_field} presents the locations of every Las Vegas (black) and Denver (orange) player on the field at particular time points in this play, with our focused player Maxx Crosby highlighted in blue.
Note that the point size for each Las Vegas defender corresponds to the estimated STRAIN in the selected frames as the play progresses.
In addition, Figure \ref{fig:fig_field} is accompanied by Figure \ref{fig:fig_crosby_curves}, which is a line graph showing how Crosby's distance from the quarterback, velocity, and STRAIN change continuously throughout the play.

@@

@@

(talk a bit about other rushers, maybe connect this with positional curves broken down by outcome - sack.)

@@

```{r}
#| label: fig_outcome_curves
#| fig.cap: "STRAIN curves for different positions by outcome"
#| fig.width: 6
#| fig.height: 6
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

@@

There are a variety of quantities we're interested in from the multilevel model fit in Section [INSERT SECTION REF]. First, Table [FIXED EFFECTS REF] displays the results for the fixed effects terms. [INSERT CONCLUSIONS ABOUT THESE VARIABLES]  Next, Table [INSERT ICC TABLE REF] displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance. While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker. This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.

>>>>

To illustrate our proposed metric STRAIN for pass rush evaluation, we use the same play from the Las Vegas Raiders and Denver Broncos game as mentioned in Section \ref{sec:data}.
Figure \ref{fig:fig_field} shows an updated version of Figure \ref{fig:fig_field_raw}, with the point size for each Las Vegas defender corresponding to the estimated STRAIN in the selected frames as the play progresses.
In addition, Figure \ref{fig:fig_field} is accompanied by Figure \ref{fig:fig_crosby_curves}, which is a line graph showing how Crosby's distance from the quarterback, velocity, and STRAIN change continuously throughout the play.

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "strain curve for unsuccessful play"
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

@@

```{r}
#| label: fig_outcome_curves
#| fig.cap: "STRAIN curves for different positions by outcome"
#| fig.width: 6.5
#| fig.height: 2.7
source(here("scripts", "08_fig_outcome_curves.R"))
fig_outcome_curves
```

@@

There are a variety of quantities we're interested in from the multilevel model fit in Section \ref{sec:methods}.

[INSERT SECTION REF]. First, Table [FIXED EFFECTS REF] displays the results for the fixed effects terms. [INSERT CONCLUSIONS ABOUT THESE VARIABLES]  Next, Table [INSERT ICC TABLE REF] displays the intraclass correlation coefficients (ICC) for the three different grouped terms, describing the proportion variance explained between the group terms in comparison to the residual variance. While the residual variance is unsurprisingly the largest value, between the three group terms, we observe the largest ICC for pass rushers, followed by the QB, and the blocker. This emphasizes how STRAIN is mostly attributable to pass rushers, but is necessary to adjust for opposition and other factors.
